---
title: "Kermit Perceptions Rank-Based Tests"
author: "Joanna Tang"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is Joanna's first message in the document.

Collaborator:
- Load tidyverse
- Read in the kermit data as "kermit"
- make some side-by-side histograms of the Score.pre for all respondents, separated by the Gender column

```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist


```

Creator: Perform rank-based comparisons using Mann-Whitney U and Wicoxon-Signed Rank

Question: Is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents?

```{r}

mwu_kermit <- kermit %>%
  wilcox.test(Score.pre ~ Gender, data = .)

# H0: There is NOT a significant difference in ranks for male and female respondents

# HA: There IS a saignificant difference in ranks

mwu_kermit

```

There is no significant difference in ranks for male and female respondents (W = 155.5, p = 0.4, alpha = 0.05).